Second-Generation Web Interface to Correcting ASR output

### 2018-03-31 2018-ftc-vancouver/webapp-anon.tex
anonymized version

\begin{filecontents}{citace.bib}
@inproceedings{kruuza2012making,
  title={Making Community and ASR Join Forces in Web Environment},
  author={Kr\r{u}za, Old{\v{r}}ich and Peterek, Nino},
  booktitle={International Conference on Text, Speech and Dialogue},
  pages={415--421},
  year={2012},
  organization={Springer}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
\end{filecontents}

@@

\begin{document}
\mainmatter              % start of a contribution
%
\title{Second-Generation Web Interface to Correcting ASR output}
%
\titlerunning{Second-Generation Web Interface to Correcting ASR output}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Old\v{r}ich Kr\r{u}za and Vladislav Kubo\v{n}}
%
\authorrunning{Kr\r{u}za, Kubo\v{n}} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Charles University\\
           Faculty of Mathematics and Physics\\
           Institute of Formal and Applied Linguistics\\
           Malostransk\'{e} n\'{a}m. 25, Prague, Czech Republic\\
           \{kruza,vk\}@ufal.mff.cuni.cz}

@@

The research was supported by SVV project number 260 453.\\
\\
This work has been using language resources stored
and distributed  by the LINDAT/CLARIN project of the Ministry of Education,
Youth and Sports of the Czech Republic (project LM2015071).

\bibliographystyle{splncs03}
\bibliography{citace}

>>>>

\begin{filecontents}{citace-anon.bib}
@inproceedings{kruuza2012making,
  title={The unnamed previous version},
  author={John Doe and Joan Doe},
  booktitle={The Example Conference},
  pages={42--4242},
  year={2012},
  organization={Example Publisher}
}
@article{codd1970relational,
  title={A relational model of data for large shared data banks},
  author={Codd, Edgar F},
  journal={Communications of the ACM},
  volume={13},
  number={6},
  pages={377--387},
  year={1970},
  publisher={ACM}
}
@article{adenot2013web,
  title={Web audio api},
  author={Adenot, Paul and Wilson, Chris and Rogers, Chris},
  journal={W3C, October},
  volume={10},
  year={2013}
}
@article{abramov2015redux,
  title={Redux},
  author={Abramov, D},
  journal={React Community, c},
  year={2015}
}
@article{hajek2007cesky,
  title={\v{C}esk\'{y} mystik Karel Mako\v{n}},
  author={Jurik H\'{a}jek},
  journal={Dingir},
  year={2007},
  volume={2007/4},
  pages={142--143},
  publisher={Dingir, s.r.o.},
  ISSN={1212-1371},
  editor={Zden\v{e}k Vojt\'{i}\v{s}ek}
}
\end{filecontents}

@@

\begin{document}
\mainmatter              % start of a contribution
%
\title{Second-Generation Web Interface to Correcting ASR output}
%
\titlerunning{Second-Generation Web Interface to Correcting ASR output}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{John Doe and Joan Doe}
%
\authorrunning{John Doe and Joan Doe} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
%\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
%Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Unnamed University\\
           Faculty of Placeholder Arts\\
           Example Institute\\
           Street 42, City, Country\\
           \{john.doe,joan.doe\}@example.com}

@@

The research was supported by Example project number 123456.\\
\\
The research was supported by Example project number 123456.\\
\\
The research was supported by Example project number 123456.

\bibliographystyle{splncs03}
\bibliography{citace-anon}
